### 2020-07-16 ISSTA/introduction.tex
small fixes

Determinism is particularly important for testing and debugging, where
being able to exactly reproduce system behavior is essential to
productivity.  Developers using a test exhibiting nondeterminism
to debug a system
face a serious challenge.
Regression testing
effectiveness can be significantly reduced if tests cover code or,
worse yet, fail only
intermittently and unpredictably.  Such behavior is
unfortunately all too common:  Gao et
al. \cite{Gao:2015:MSU:2818754.2818764} observed coverage differences
of up to 184 LOC for the same test, and false positive rates
as high as 96\%.  Nondeterminism is problematic for
developers, who want to  assume that library code behaves in a  predictable fashion; nondeterminism is
vexing in debugging; nondeterminism is \emph{often disastrous} for large-scale 
automated testing.

@@

Complex
modern software systems usually include a large set of
\emph{regression tests}.  A regression test suite is a
set of tests that can be run every time code
is modified, to ensure that the modification has not broken the system.  \emph{Flaky tests} \cite{miccoflaky} are regression
tests that fail in an intermittent, unreliable fashion.  The essence of a flaky
test is that, for the same snapshot of test code and code under test, it sometimes fails and sometimes passes: the pass/fail result (disposition) of the
test is not a deterministic property of the test code, code under
test, and testing environment.  This produces three serious
problems: first, a flaky test often wastes developer time and delays
software changes by forcing the investigation of \emph{correct} code-under-test.  Second, failures in flaky tests are often ignored, and therefore serious software faults missed.  Finally, to mitigate the problem, flaky tests are often
run multiple times, wasting computing resources and
delaying code changes.  Flaky tests are, for us, simply a special case the 
\emph{horizontal} nondeterminism 
described below.  Our focus is on detecting sources of 
flaky-ness, \emph{before} they propagate.
\begin{comment}
  As an analogy, we note that  a canary in a coal mine is of
little use if canaries frequently become ill for reasons unrelated to
the presence of toxic gases.  Mining may stop for no good reason, or
miners may learn to ignore the canary, leading to tragedy; a third,
more ``practical'' option is that miners may carry so many redundant
canaries into the coal mine that canary-care itself becomes a serious burden.
\end{comment}

>>>>

Determinism is particularly important for testing and debugging, where
being able to exactly reproduce system behavior is essential to
productivity.  Developers using a test exhibiting nondeterminism
to debug a system
face a serious challenge.
Regression testing
effectiveness can be significantly reduced if tests cover code or,
worse yet, fail, only
intermittently and unpredictably.  Such behavior is
unfortunately all too common:  Gao et
al. \cite{Gao:2015:MSU:2818754.2818764} observed coverage differences
of up to 184 LOC for the same test, and false positive rates
as high as 96\%.  Nondeterminism is problematic for
developers, who want to  assume that library code behaves in a  predictable fashion; nondeterminism is
vexing in debugging; nondeterminism is \emph{often disastrous} for large-scale 
automated testing.

@@

Complex
modern software systems usually include a large set of
\emph{regression tests}.  A regression test suite is a
set of tests that can be run every time code
is modified, to ensure that the modification has not broken the system.  \emph{Flaky tests} \cite{miccoflaky} are regression
tests that fail in an intermittent, unreliable fashion.  The essence of a flaky
test is that, for the same snapshot of test code and code under test, it sometimes fails and sometimes passes: the pass/fail result (disposition) of the
test is not a deterministic property of the test code, code under
test, and testing environment.  This produces three serious
problems: first, a flaky test often wastes developer time and delays
software changes by forcing the investigation of \emph{correct} code-under-test.  Second, failures in flaky tests are often ignored, and therefore serious software faults missed.  Finally, to mitigate the problem, flaky tests are often
run multiple times, wasting computing resources and
delaying code changes.  Flaky tests are, for us, simply a special case
of the 
\emph{horizontal} nondeterminism 
described below.  Our focus is on detecting sources of 
flaky-ness, \emph{before} they propagate.
\begin{comment}
  As an analogy, we note that  a canary in a coal mine is of
little use if canaries frequently become ill for reasons unrelated to
the presence of toxic gases.  Mining may stop for no good reason, or
miners may learn to ignore the canary, leading to tragedy; a third,
more ``practical'' option is that miners may carry so many redundant
canaries into the coal mine that canary-care itself becomes a serious burden.
\end{comment}
